*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "timeMinSec" to "time_min_sec";

and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`timeMinSec` ) and maximal (`timeMaxSec`) time points
to be included (in seconds).

>>>>

and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`time_min_sec` ) and maximal (`timeMaxSec`) time points
to be included (in seconds).
